Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-11-18 talk/pepm2011/paper.tex
add dynamic typing reference

A related optimization is also that of deforestation
\cite{wadler_deforestation:_1988,gill_short_1993} which tries to remove
intermediate lists or trees in functional languages. More explicitly geared at
optimizing boxing is boxing analysis \cite{jrgensen_calculus_1996} which tries
to fully remove pairs of calls to box/unbox in a functional language.

%xxx:
%partially static data structures: kenichi asai's thesis?

%xxx: 
%Other related work is compile-time garbage collection \cite{mazur_practical_2001}, which
%tries to ....;
%  separation logic
  %; John Hughes: type specialization

>>>>

A related optimization is also that of deforestation
\cite{wadler_deforestation:_1988,gill_short_1993} which removes intermediate
lists or trees in functional languages. A more general approach is boxing
analysis \cite{jrgensen_calculus_1996} which optimizes pairs of calls to
box/unbox in a functional language. Similarly, "dynamic typing"
\cite{Henglein:1994:DTS:190865.190867} tries to remove dynamic type coercions
in a dynamically typed lambda-calculus. All these optimizations work by
analyzing the program before execution, which makes them unsuitable for dynamic
languages like Python, where almost nothing can be inferred purely by looking
at the source code.
